Models of lens candidates from Space Warps CFHTLS

### 2016-12-27 parts/massmodel.tex
editing

Alongside is a synthetic image produced by modelling.  In it, the
fitted lensed images are shown in colour, while the lensing galaxy and
extraneous objects have been reduced to grayscale.
(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
synthetic image from another model of the same system.) These two
panels are qualitative and display no units, and moreover, the mutual
alignment of the two panels is only approximate.

>>>>

Alongside is a synthetic image produced by modelling.  In it, the
fitted lensed images are shown in colour, while the lensing galaxy and
extraneous objects have been reduced to grayscale.
(Figure~\figref{synthimg} in Appendix~\ref{subsec:sourcefit} shows a
synthetic image from another model of the same system.) These two
panels are qualitative and display no units, and moreover, the mutual
alignment of the two panels is only approximate.

### 2016-12-27 parts/morph.tex
editing

Figure~\ref{fig:markedup} shows cutouts of the Space~Warps image,
marked up with a spaghetti diagram.

The lenses are arranged as follows.
$$
\begin{matrix}
\rm SW58 & \rm SW28 & \rm SW57 \\
\rm SW05 & \rm SW42 & \rm SW19 \\
\rm SW09 & \rm SW29 & \rm SW02
\end{matrix}
$$ 
$\{${\em Panels will be labelled, and this little table removed.}$\}$

>>>>

Figure~\ref{fig:splinput} shows cutouts of the Space~Warps image,
marked up with a spaghetti diagram.

### 2016-12-27 parts/summary.tex
editing

Table~\ref{tab:models} shows a summary of the analysis for many candidates.
Missing rows are due to photometry data not available.

Accordingly the the characterisation of each modelled system is
(i)~according to the image morphology and how clear or indistinct it
is, (ii)~whether the mass map and synthetic lensed image appear to be
plausible, and (iii)~how the model mass compares with the estimated
stellar and full-halo masses.

>>>>

This work follows up on lens candidates reported in
\cite{2016MNRAS.455.1191M} from citizen-science volunteers, with
modelling.  Volunteers role is collaborative.  No robotic competitors.

Table~\ref{tab:models} characterises each modelled system is
(i)~according to the image morphology and how clear or indistinct it
is, (ii)~whether the mass map and synthetic lensed image appear to be
plausible, and (iii)~how the model mass compares with the estimated
stellar and full-halo masses.  Missing rows are due to photometry data
not available.

Figure~\ref{fig:stelmass} summarises the properties of the lens
candidates
